---
title: "Prepae metadata file for asthma data"
author: "TB"
date: "7/28/2017"
output: html_document
---
```{r}
library("tidyverse")
library("stringr")
library("readr")
library("plotly")
library("ggplot2")
library("neutrominer")
library("magrittr")
library("caret")
library("AppliedPredictiveModeling")
source("utilities.r")
```

# Load data
Analysis folder and tracked data 
```{r}
analysis_folder <- "../../analysis/20171001_cp3/"
csv_tracks <- 'tracks_cp.csv'
csv_single_cells <- "Tracked_detectedNeutros.csv"

csv_profile <- "profiles.csv"
```

# Metadata 
```{r}
strata <- c('Metadata_attractant','Metadata_concentration','Metadata_condition',
            'Metadata_date','Metadata_dose','Metadata_id')
```

# read tracking data 
```{r}
population <- read_csv(file.path(analysis_folder, csv_tracks))

tracks <- population %>%  
  filter(Track_Life_Time > 19) %>% 
  filter(complete.cases(.))

tracks %>% group_by(Metadata_attractant, Metadata_id) %>% summarise(xfmi = mean(Track_xFMI))
```

# Load single cell data 
The output of CellProfiler track module is loaded as CSV, tracked using cytominer::track and 
stored in the data folder as "track.csv". 
```{r}
# load csv files from all sub folders 
df <- read_single_cell_data(analysis_folder, csv_single_cells) %>%
  mutate(Metadata_timePoint = Metadata_frame) %>%
  dplyr::mutate(Metadata_timePoint = as.double(Metadata_timePoint))
```

# Filter invalid paths 
The data frame tracks only includes trajectories with a life time =>20 frames
(>=10 Minutes). All small tracks are removed from the single cell data, too.
```{r}
morphology <- semi_join(df, tracks, by = c(strata,"TrackObjects_Label"))
```

# Define feature columns
```{r}
feature_cols <- setdiff(
  colnames(morphology) %>%
  stringr::str_subset("^AreaShape_|^RadialDistribution|^Track|^Texture"),
  "TrackObjects_Label")
```

# Profiling 
Create profiles / aggregate trajectories
```{r}
bad_columns <- cytominer::drop_na_columns(
  population = morphology,
  variables = feature_cols
)

profile <-
  cytominer::aggregate(
    population = morphology %>% select(c(strata,"TrackObjects_Label",setdiff(feature_cols, bad_columns))),
    variables = setdiff(feature_cols, bad_columns),
    strata = c(strata,"TrackObjects_Label"),
    operation = "mean"
  ) 
```


# Store as CSV
```{r}
write_csv(profile, file.path(analysis_folder, csv_profile))
```