---
title: "Prepae metadata file for asthma data"
author: "TB"
date: "7/28/2017"
output: html_document
---
```{r}
library("tidyverse")
library("stringr")
```

# 

Define folder with time lapse experiments. All folders start with the data of the experiment and are extracted using dir.
```{r}
image_folder <-  "/Users/tbecker/Documents/2017_09_migration/images/"

dir_list <- dir(image_folder,pattern = "^[0-9]")
```

All folder follow the pattern 201612a_kira0094_ltb4_xxng_fn_asthma with

* Metadata_date = 201612a
* Metadata_id = kira0094
* Metadata_matrix = fn
* Metadata_condition = (asthma | asthma-control | onedonor ) 
* Metadata_attractant = ltb4
* Metadata_concentration = xxng

The metadata is extracted from the name using str_split and we create a tibble / data frame containing the metadata information and path information for all time lapse experiments.  

```{r}
metadata_path <-  dir_list %>% 
  str_split(.,"_") %>%
  unlist() %>%
  matrix(., nrow = length(dir_list), byrow = TRUE) %>%
  as_tibble() %>%
  rename("Metadata_date" = V1) %>%
  rename("Metadata_id" = V2) %>%
  rename("Metadata_attractant" = V3) %>%
  rename("Metadata_concentration" = V4) %>% 
  rename("Metadata_matrix" = V5) %>%
  rename("Metadata_condition" = V6) %>% 
  mutate(full_path = file.path(image_folder,unlist(dir_list))) %>%
  mutate(path_name = unlist(dir_list)) 
```

To combine the single images corresponding to one experiment with the metadata and path information, a file list by executing the command 

```find . -name *png  > image_list.csv```

in the image folder. Each entry stores the path and the image name. Example:

```./20130424_FN_cont_bd0036/20130424_FN_cont_0000.png```


```{r}
file_list <- read_csv(file.path(image_folder,"image_list.csv")) 

metadata_files <- tibble(path_name = unlist(lapply(file_list, dirname)), 
                         file_name = unlist(lapply(file_list, basename))) %>%
  mutate(Metadata_frame = as.integer(str_sub(file_name,-7,-4))) %>%
  mutate(path_name = str_sub(path_name,3,-1)) %>%
  print

metadata_files %>% group_by(path_name) %>% summarise(s= n()) %>% print
```

Both  data frames are combined and and an additional columns is inserted to make the data / file_list  compatible with the available CP pipelines.   

```{r}
metadata <- left_join(metadata_files, metadata_path, by = "path_name") %>%
  mutate(Metadata_dose = 'None') %>%
  rename(PathName_neutrophils = full_path) %>%
  rename(FileName_neutrophils = file_name) %>%
  select(Metadata_date, Metadata_attractant, Metadata_concentration, Metadata_id, Metadata_condition, Metadata_dose, Metadata_frame, PathName_neutrophils, FileName_neutrophils) %>%
  print
```
```{r}
write_csv(metadata, file.path(image_folder,"file_list.csv"))
```
