---
title: "Prepae metadata file for asthma data"
author: "TB"
date: "7/28/2017"
output: html_document
---
```{r}
library("tidyverse")
library("stringr")
library("readr")
library("plotly")
library("ggplot2")
library("neutrominer")
library("magrittr")
library("caret")
library("AppliedPredictiveModeling")
source("../utilities.r")
```

# Load data
Analysis folder and tracked data 
```{r}
analysis_folder <- "../../../analysis/20171006/"
csv_tracks <- "tracks_cp.csv"
csv_profile <- "profiles.csv"

csv_clean_tracks <- "normalized_tracks.csv"
csv_clean_profile <- "normalized_profile.csv"

```

# Metadata 
```{r}
strata <- c('Metadata_condition','Metadata_date','Metadata_dose','Metadata_id','Metadata_matrix', 'TrackObjects_Label')
```

# read tracking data 
```{r}
migration <- read_csv(file.path(analysis_folder, csv_tracks)) %>% 
  filter(Track_Life_Time > 19)

profile <- read_csv(file.path(analysis_folder, csv_profile))
```
# select features 
Select feature names and remove double entries marked with a _1 (these are introduced by CP)
```{r}
feature_cols <- base::setdiff(
  colnames(profile) %>%
    stringr::str_subset("^Area|^Radial|^Texture|^Track"),
  colnames(profile) %>%
    stringr::str_subset("_1")
)

feature_cols <- setdiff(feature_cols, "TrackObjects_Label")
```

# remove na columns
```{r}
feature_cols <- setdiff(feature_cols, 
  cytominer::drop_na_columns(
    population = profile,
    variables = feature_cols,
    cutoff = 0
  )
)
```

# remove na rows
```{r}
clean_profile <- cytominer::drop_na_rows(
  population = profile, 
  variables = feature_cols
  )
```

# remove zero variance features
```{r}
feature_cols <- setdiff(
  feature_cols, 
  cytominer::variance_threshold(
    sample = clean_profile, 
    variables = feature_cols
  )
)
```

# remove correlated feature 
We use the findCorrelation method from the caret package 
```{r}
feature_cols_final <- setdiff(feature_cols,
  clean_profile %>% 
  ungroup() %>% 
  select_(.dots = feature_cols) %>%
  as.matrix() %>%
  cor(.) %>%
  findCorrelation(.,cutoff = 0.95, names = TRUE)
)
```

# normalize morphological profiles  
```{r}
normalized_profile <- cytominer::normalize(
    population = clean_profile,
    variables = feature_cols_final,
    strata =  "Metadata_id",
    sample = clean_profile %>% filter(Metadata_condition == "vehi"),
    operation = "robustize"
)

normalized_profile %<>% 
  select_(.dots = c(strata, feature_cols_final))
```


# check for bad features
```{r}
feature_cols_bad <- cytominer::drop_na_columns(
  population = normalized_profile, 
  variables = feature_cols_final, 
  cutoff = .05
)

normalized_profile_final <- normalized_profile %>% 
  select_(.dots = c(strata, setdiff(feature_cols_final, feature_cols_bad)))
```

# -----------------------------------------------------------------------------
# normalize migration profiles
```{r}
migration_features <- colnames(migration) %>%
    stringr::str_subset("^Track") 

migration_features <- setdiff(
  migration_features, 
  c("TrackObjects_Label","Track_One_Cell","Track_Length","Track_Life_Time","Track_Sector",
    "Track_Positive_Sector","Track_Negative_Sector","Track_Neutral_Sector_Up","Track_Neutral_Sector_Down")
)
  
normalized_migration <- cytominer::normalize(
   population = migration,
    variables = migration_features,
    strata =  "Metadata_id",
    sample = migration %>% filter(Metadata_condition == "vehi"),
    operation = "robustize"
)

```


# check for bad features
```{r}
feature_cols_bad <- cytominer::drop_na_columns(
  population = normalized_profile, 
  variables = feature_cols_final, 
  cutoff = .05
)
```


# Store as CSV
```{r}
write_csv(normalized_profile_final, file.path(analysis_folder, csv_clean_profile))
write_csv(normalized_migration, file.path(analysis_folder, csv_clean_tracks))
```