---
title: "load_data"
author: "TB"
date: "5/15/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("stringr")
library("readr")
library("plotly")
library("ggplot2")
library("neutrominer")
library("magrittr")
library("corrplot")
library("Rtsne")
```

# Load data
Analysis folder and tracked data 
```{r}
analysis_folder <- "../../../analysis/20171006/"

csv_clean_tracks <- "normalized_tracks.csv"
csv_clean_profile <- "normalized_profile.csv"

profile <- read_csv(file.path(analysis_folder, csv_clean_profile))
```

# Metadata 
```{r}
strata <- c('Metadata_condition','Metadata_date','Metadata_dose','Metadata_matrix','Metadata_id')
```

# feature columns
```{r}
all_feature_cols <- colnames(profile) %>%
    stringr::str_subset("^Area")
  
bad_cols <- cytominer::drop_na_columns(
  population = profile ,
  variables = all_feature_cols,
  cutoff = 0
)

feature_cols <- setdiff( 
  colnames(profile) %>%
    stringr::str_subset("^Area"),
  bad_cols
)
```

# remove zero variance features 
```{r}
bad_cols_variance <- cytominer::variance_threshold(
  sample = profile,
  variables = feature_cols
)

feature_cols <- setdiff( 
feature_cols,
  bad_cols_variance
)
```

# Aggregate data to experiments
```{r}
aggregated <- cytominer::aggregate(
  population = profile,
  variables = feature_cols,
  strata = strata,
  operation = "mean"
)

feature_cols_aggregated <- setdiff( 
  colnames(aggregated) %>%
    stringr::str_subset("^Area"),
  "RadialDistribution_ZernikePhase_neutrosIlluCorrected_2_0_mean"
)
```

# Visualize data using tsne and pca
```{r}
HEM <- profile %>% 
  filter(Metadata_matrix %in% c("FN","HEM"))

train <- HEM %>% 
  filter(Metadata_matrix %in% c("FN","HEM")) %>%
  ungroup() %>% 
  select_(.dots = feature_cols)

tsne <- Rtsne(train, perplexity = 50, verbose = TRUE, max_iter = 500, theta = 0, pca_scale = TRUE, initial_dims = 52)

```

```{r}
Y <- as.data.frame(tsne$Y)

  df = cbind(as.data.frame(Y),
             as.data.frame(profile %>% filter(Metadata_matrix %in% c("FN","HEM"))))

  print(ggplot(data = df %>% filter(Metadata_condition %in% c("vehi","pred")), aes(x = V1, y = V2, size = 20, shape = Metadata_matrix, color = factor(Metadata_condition))) +
      geom_point() +
      xlab("") + 
      ylab("") +
      ggtitle("t-SNE") +
      guides(colour = guide_legend(override.aes = list(size = 6))) +
      theme_light(base_size = 20) +
      theme(axis.text.x = element_blank(),
            axis.text.y = element_blank()) + 
      labs(title = sprintf('tsne of morphological profiles, perplexity %i', tsne$perplexity )))  
   
```
  print(ggplot(data = df %>% filter(Metadata_condition %in% c("pred")), aes(x = V1, y = V2, size = 10, color = factor(Metadata_id))) +
      geom_hex() +
      xlab("") + 
      ylab("") +
      ggtitle("t-SNE") +
      guides(colour = guide_legend(override.aes = list(size = 6))) +
      theme_light(base_size = 20) +
      theme(axis.text.x = element_blank(),
            axis.text.y = element_blank()) + 
      labs(title = sprintf('Migration clustered with perplexity %i', tsne$perplexity ))) 
   
  
```