---
title: "load_data"
author: "TB"
date: "5/15/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("stringr")
library("readr")
library("plotly")
library("ggplot2")
library("neutrominer")
library("magrittr")
library("corrplot")
library("Rtsne")
source("../utilities.r")
source("../windrose.r")
```

# Load data
Analysis folder and tracked data 
```{r}
analysis_folder <- "../../../analysis/20171006/"

csv_clean_tracks <- "tracks_cp.csv"
csv_clean_profile <- "normalized_profile.csv"

profile <- read_csv(file.path(analysis_folder, csv_clean_profile))
tracks <- read_csv(file.path(analysis_folder, csv_clean_tracks))
```

```{r}
profile %>% 
  ungroup() %>% 
  filter(Metadata_condition %in% c("vehi","pred")) %>%
  group_by(Metadata_condition,Metadata_matrix) %>%
   summarise(
    n_tracks = n(),
    #mean_speed = mean(Track_Speed), sd_speed = sd(Track_Speed),
    #mean_xfmi =  mean(Track_xFMI), sd_xfmi  = sd(Track_xFMI),
    #mean_directionality = mean(Track_Directionality), sd(Track_Directionality),
    n = n()
  ) 

  
  
```

# Metadata 
```{r}
strata <- c('Metadata_condition','Metadata_date','Metadata_dose','Metadata_id','Metadata_matrix')
```

# feature columns
```{r}
feature_cols <- colnames(profile) %>%
    stringr::str_subset("^Area")
```

# drop na columns
```{r}
feature_cols <- setdiff(
  feature_cols,
  cytominer::drop_na_columns(
    population = profile,
    variables = feature_cols
  )
)
```

# cluster data sets
cytominer is used to extract some subpopulations 
```{r}
reference <- profile %>% 
  filter(Metadata_condition %in% c("vehi") ) %>% 
  filter(Metadata_matrix %in% c("HEM","FN") ) 
  #select_(.dots = feature_cols)

population <- profile %>% 
  filter( Metadata_condition %in% c("pred") ) %>% 
  filter(Metadata_matrix %in% c("FN","HEM") ) 
  #select_(.dots = feature_cols)

set.seed(42)

clusteranalysis <- cytominer::extract_subpopulations(
  population = population, 
  reference = reference, 
  variables = feature_cols, 
  k = 10
  ) %>% print
```
# collect clustered data
The results for the clustering are stored in two data frames 
1. clusteranalysis$population_clusters and 
2. clusteranalysis$reference_clusters
Both are collected in the data frame subpopulation
```{r}
subpopulation <- rbind(clusteranalysis$population_clusters, clusteranalysis$reference_clusters)
```

# grouped subpopulations 
Based on the given clusting the function grouped_clusters calculates the cluster distribution for a given set of grouping variables
```{r}
grouped_clusters <- function(population, strata) {
  result <- left_join(
    population,
    population %>% 
      group_by_(.dots = strata) %>%
      summarise(cluster_size = n()), 
    by = strata
  )  %>% 
    group_by_(.dots = c(strata, "cluster_id")) %>%
    summarise(no_tracks = n(), cluster_size = mean(cluster_size)) %>% 
    mutate(fraction = no_tracks / cluster_size) 
}
```

Call grouped_clusters for our data frame.
```{r}
strata = c("Metadata_condition","Metadata_matrix")

clusters <- grouped_clusters(
  population = subpopulation,
    strata = c(strata,"Metadata_id")
    ) %>%
  mutate(id = paste(Metadata_matrix, Metadata_condition, sep = ' ')) %>% print
```

# visualize different cluster distribution
As histogram next to each other 
```{r}
cluster_plot <- clusters %>%
  rename(condition = "Metadata_condition")

cluster_plot[cluster_plot=="vehi"]<-"None"
cluster_plot[cluster_plot=="pred"]<-"Prednisolone"

ggplot(data = cluster_plot ) + 
  aes(x = cluster_id, y = fraction, fill = condition) + 
  geom_col(position = "dodge") + 
  facet_wrap(~ Metadata_matrix)

ggsave("cluster_histogram.png")
```

stagged 
```{r}
ggplot(data = clusters) + 
  aes(x = id, y = fraction, color = cluster_id, fill = cluster_id) +
  geom_col()
```

# add cluster centers to data points 
The data is splitted in 
```{r}
population_tracks <- tracks %>% 
  filter( Metadata_condition %in% c("vehi","pred") ) %>% 
  filter( Metadata_matrix %in% c("FN","HEM") ) 
```

# Join morphological data and migration data
```{r}
population_tracks_cluster <- left_join(
  subpopulation,
   population_tracks, 
  by =  c("Metadata_matrix", "Metadata_condition", "Metadata_id","TrackObjects_Label")  
  ) %>%
  group_by_(.dots = c("Metadata_matrix", "Metadata_condition","Metadata_id","cluster_id"))
```

# Patient based distribution 
```{r}
population_tracks_cluster %>% 
  summarise(
    mean_speed = mean(Track_Speed),
    mean_xfmi =  mean(Track_xFMI),
    mean_directionality = mean(Track_Directionality)
  ) %>% 
  filter(
    cluster_id %in% c(4,8,11,13,19,20),
    Metadata_condition == "vehi"
    )
```

```{r}
population_tracks_cluster %>%
  ungroup() %>% 
  filter(
    cluster_id %in% c(4,8,11,13,19,20),
    Metadata_matrix %in% c("FN")
    ) %>%
  group_by_(.dots = c("Metadata_condition","Metadata_matrix","cluster_id")) %>%
   summarise(
    mean_speed = mean(Track_Speed), sd_speed = sd(Track_Speed),
    mean_xfmi =  mean(Track_xFMI), sd_xfmi  = sd(Track_xFMI),
    mean_directionality = mean(Track_Directionality), sd(Track_Directionality),
    n = n()
  ) 
```
classical analysis
```{r}
population_tracks_cluster %>% 
  ungroup() %>% 
  filter(Metadata_condition %in% c("vehi","pred")) %>%
  group_by(Metadata_condition,Metadata_matrix) %>%
   summarise(
    n_tracks = n(),
    mean_speed = mean(Track_Speed), sd_speed = sd(Track_Speed),
    mean_xfmi =  mean(Track_xFMI), sd_xfmi  = sd(Track_xFMI),
    mean_directionality = mean(Track_Directionality), sd(Track_Directionality)
  ) 

```

# Extract trajectories
Extract tracks corresponsing to the 5 cells that are closest to the clusters 4,5,7,9. We use the reference run in FN with condition == "vehicle". We use the 
* cluster_id and the 
* dist_to_cluster
to find the best trajectories.
```{r}
close_to_cluster_center <- subpopulation %>% 
  filter(
    Metadata_matrix == "FN",
    Metadata_condition == "vehi",
    cluster_id %in% c(4,5,7,9)
    ) %>% 
  select_(.dots = c(strata,"Metadata_id", "cluster_id", "dist_to_cluster", "TrackObjects_Label" )) %>%
  ungroup() %>% 
  group_by(cluster_id) %>%
  arrange(dist_to_cluster) %>%
  slice(seq(1,3,1)) %>% 
  print
  
```
Load single cell data 
```{r}
single_cell_data <- read_csv(file.path(analysis_folder,'Tracked_detectedNeutros.csv'))
```
Now we merge the single cell data and the tracks closest to the cluster centers
```{r}

complete_data <- left_join(
  close_to_cluster_center, 
  single_cell_data %>% 
    add_metadata_matrix, 
  by =  c(strata,"Metadata_id", "TrackObjects_Label" )
  ) 

complete_data %>% select(Metadata_condition, Metadata_matrix, Metadata_id, Metadata_dose, Metadata_frame, TrackObjects_Label, AreaShape_Center_X, AreaShape_Center_Y, cluster_id, TrackObjects_Lifetime ) %>% 
  group_by_(.dots = c(strata,"Metadata_id", "TrackObjects_Label")) %>% 
  arrange(-Metadata_frame) %>%
  slice(1)

```
Plot velocity vs area
```{r}
ggplot(data = subpopulation) +
  aes(x = )
```