---
title: "06_combine_migration_and_CP_features"
author: "TB"
date: "7/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("magrittr")
library("knitr")
library("corrplot")
library("stringr")
library("heatmaply")
library("SNFtool")
source("../utilities.R")
library("reshape2")
```


# Load data
Analysis folder and tracked data 
```{r}
analysis_folder <- "../../../analysis/20171006/"

csv_clean_tracks <- "tracks_cp.csv"
csv_clean_profile <- "normalized_profile.csv"
```

# read and arrange data to make sure they are in the same order
```{r}
profile <- read_csv(file.path(analysis_folder, csv_clean_profile)) %>%
  arrange(Metadata_matrix, Metadata_condition, Metadata_id)

tracks <- read_csv(file.path(analysis_folder, csv_clean_tracks)) %>%
  arrange(Metadata_matrix, Metadata_condition, Metadata_id) %>%
  filter(Track_Length > 19)
```


# Metadata 
```{r}
strata <- c('Metadata_condition','Metadata_date','Metadata_dose','Metadata_id','Metadata_matrix')
```


# feature columns
```{r}
feature_cols <- colnames(profile) %>%
    stringr::str_subset("^Area")
```

# drop na columns
```{r}
feature_cols <- setdiff(
  feature_cols,
  cytominer::drop_na_columns(
    population = profile,
    variables = feature_cols
  )
)
```

# Collapse data per patient
```{r}
aggregated_morphology <- cytominer::aggregate(
    population = profile,
    variables = feature_cols,
    strata = strata,
    operation = "median"
  ) %>% collect()
```

# update features 
```{r}
feature_morphology <- colnames(aggregated_morphology) %>% 
   stringr::str_subset("^Area") %>%
  print
```

# set rownames and calculate distance matrix 
```{r}
row.names(aggregated_morphology) <- aggregated_morphology %>% 
  mutate(id = str_c(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose, sep = ' ')) %>%
  extract2("id")

dist_morphology <- aggregated_morphology %>%
  ungroup() %>%
  #filter(Metadata_matrix == "HEM") %>%
  select_(.dots = feature_morphology) %>%
  dist() %>%
  as.matrix()
```


# migration 
```{r}
feature_cols_migration = c("Track_Speed","Track_Speed_Y","Track_Speed_X","Track_xFMI","Track_yFMI","Track_Directionality","Track_Distance_Traveled","Track_CI") 

aggregated_migration <- cytominer::aggregate(
    population = tracks,
    variables = feature_cols_migration,
    strata = strata,
    operation = "median"
  ) %>% collect()

feature_migration <- colnames(aggregated_migration) %>%
  stringr::str_subset("^Track") %>%
  print

row.names(aggregated_migration) <- aggregated_migration %>% 
  mutate(id = str_c(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose, sep = ' ')) %>%
  extract2("id")

dist_migration <- aggregated_migration %>%
  ungroup() %>%
  #filter(Metadata_matrix == "HEM") %>%
  select_(.dots = feature_migration) %>%
  dist(.)  %>%
  as.matrix()
```

# Calculate affinity matrices using SNFtool package
```{r}
W1 <- affinityMatrix(dist_morphology, K = 20, sigma = 0.5)
W2 <- affinityMatrix(dist_migration, K = 20, sigma = 0.5)
```

# Display affinity matrix for morgphological features 
```{r}
displayClustersWithHeatmap(W1, spectralClustering(W1, K = 5))
```
# Display affinity matrix for migration features 
```{r}
displayClustersWithHeatmap(W2, spectralClustering(W2, K = 5))
```

```{r}
sigma = 0.5
for (sigma in seq(0.3, 0.7, 0.1)) {
  for (neighbours in seq(5,20,5)) {
    
    W1 <- affinityMatrix(dist_morphology, K = neighbours, sigma = sigma)
    W2 <- affinityMatrix(dist_migration, K = neighbours, sigma = sigma)
    W = SNF(list(W1,W2), neighbours, 40)
    
    
    row.names(W) <- aggregated_migration %>% 
      mutate(id = str_c(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose, sep = ' ')) %>%
      extract2("id")
    displayClustersWithHeatmap(W, spectralClustering(W, K = 10))
  }
}
```


```{r}
metadata_rows <- aggregated_migration %>% 
  ungroup() %>%
  select_(.dots = strata) 

group_by = c("Metadata_matrix", "Metadata_condition")

fraction_strong_affinity(W,metadata_rows, group_by)

affinity = tibble()
for (sigma in seq(.1, 1, .1)) {
  for (neighbours in seq(2,15,1)) {
   
    W1 <- affinityMatrix(dist_morphology, K = neighbours, sigma = sigma)
    W2 <- affinityMatrix(dist_migration, K = neighbours, sigma = sigma)
    W = SNF(list(W1,W2), neighbours, 20)
    
    affinity <-  fraction_strong_affinity(W,metadata_rows, group_by) %>%
      mutate(sigma = sigma, K = neighbours) %>%
      rbind(.,affinity)
  }
  print(c(sigma,neighbours))
}
```

```{r}
# remove affinity values close to zero
df <- affinity %>%
  filter(sigma > 0.02)

ggplot(df, aes(x = sigma, y = K)) +
  geom_raster(aes(fill = mean_affinity)) +
  scale_fill_gradient(low = "white", high = "red") +
  theme_bw() + theme(axis.text.x=element_text(size=9, angle=0, vjust=0.3),
                     axis.text.y=element_text(size=9),
                     plot.title=element_text(size=11))

ggsave("mean_affinity.png",device = "png")
```

ggplot(df, aes(x = sigma, y = K)) +
  geom_raster(aes(fill = threshold)) +
  scale_fill_gradient(low = "white", high = "red") + 
  theme_bw() + theme(axis.text.x=element_text(size=9, angle=0, vjust=0.3),
                     axis.text.y=element_text(size=9),
                     plot.title=element_text(size=11))

ggsave("null_threshold.png",device = "png")

ggplot(df, aes(x = sigma, y = K)) +
  geom_raster(aes(fill = fraction_strong)) +
  scale_fill_gradient(low = "white", high = "red") + 
  theme_bw() + theme(axis.text.x=element_text(size=9, angle=0, vjust=0.3),
                     axis.text.y=element_text(size=9),
                     plot.title=element_text(size=11)) + 
  labs( y = "neighbours K")

ggsave("fraction_strong.png",device = "png")
```
```{r}
affinity %>% 
  arrange(-fraction_strong) %>%
  slice(1:40)
  print()
```

```{r}
 fraction_strong_affinity(W1,metadata_rows, group_by)
 fraction_strong_affinity(W2,metadata_rows, group_by)
```
```{r}
  W1 <- affinityMatrix(dist_cp, K = 4, sigma = 0.94)
    W2 <- affinityMatrix(dist_migration, K = 4, sigma = 0.94)
    W = SNF(list(W1,W2), 4, 20, parallel = FALSE)
    
    
    row.names(W) <- aggregated_migration %>% 
      mutate(id = str_c(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose, sep = ' ')) %>%
      extract2("id")
    displayClustersWithHeatmap(W, spectralClustering(W, K = 10))
```


#################################################

This time we use the data collapsed to tracks to calculate the affinity matrix


```{r}
dist_tracks_cp <- population_cp %>%
  ungroup() %>%
  filter(Metadata_matrix == "HEM") %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_id == "BD0069" ) %>%
  select_(.dots = feature_cp) %>%
  dist() %>%
  as.matrix()


dist_tracks_migration <- population_migration %>%
  ungroup() %>%
  filter(Metadata_matrix == "HEM") %>%
  filter(Metadata_condition == "CP17") %>%
    filter(Metadata_id == "BD0069" ) %>%
  select_(.dots = feature_migration) %>%
  dist() %>%
  as.matrix()

```


```{r}
K = 10
sigma = 1

W1_tracks <- affinityMatrix(dist_tracks_cp, K = K, sigma = sigma)
W2_tracks <- affinityMatrix(dist_tracks_migration, K = K, sigma = sigma)

displayClustersWithHeatmap(W1_tracks, spectralClustering(W1_tracks, K = 6))
displayClustersWithHeatmap(W2_tracks, spectralClustering(W2_tracks, K = 6))

W = SNF(list(W1_tracks,W2_tracks), K, 20, parallel = FALSE)

row.names(W) <- population_migration %>% 
  filter(Metadata_matrix == "HEM") %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_id == "BD0069" ) %>%
  mutate(id = str_c(Metadata_dose, TrackObjects_Label_30, sep = ' ')) %>%
  extract2("id")
displayClustersWithHeatmap(W, spectralClustering(W, K = 24))

```
